Comparing Optimization Algorithms in the Fitting of Linear Mixed Models: Evaluating Speed and Accuracy using \pkg{lme4} in R and \pkg{lmm} in Julia

### 2015-09-01 inst/doc/Paper.Rnw

<<results=tex>>=
print(xtable(subset(res, opt=="NLOPT_LN_Nelder_Mead" & excess > 0.005)[c(1,2,3,5,6,7,8)]),floating=FALSE, table.placement="H")
@

@@

@@

>>>>

<<results=tex>>=
print(xtable(subset(res, opt=="NLOPT_LN_NELDERMEAD" & excess > 0.005)[c(1,2,3,5,6,7,8)]),floating=FALSE, table.placement="H")
@

@@

<<results=tex>>=
print(xtable(subset(res, opt=="NLOPT_LN_SBPLX" & excess > 0.005)[c(1,2,3,5,6,7,8)]),floating=FALSE, table.placement="H")
@

@@

<<results=tex>>=
print(xtable(subset(res, opt=="LN_BOBYQA" & dsname == "kb07")[c(1,2,5,6,7,9)]),floating=FALSE, table.placement="H")
@

\subsection[Relative Speed]{Relative Speed}

We plot the time to convergence, relative to LN_BOBYQA and on a logarithmic scale, for each algorithm.

PLOT

Many of the cases where LN_BOBYQA is slower than other algorithms are simple problems that converge in less than 1/5 of a second for most algorithms.

We will declare a data set to be non-simple if at least one of the models fit to the data took more than 0.2 seconds to convergence with LN_BOBYQA.

<<results=tex>>=
print(xtable(subset(res, opt=="LN_BOBYQA" & time >= 0.2)[c("dsname","time","n","np","models")]),floating=FALSE, table.placement="H")
@
